### 2024-08-11 doc/Thesis/chapter/06-outlook.tex
start doing todo.md
nearly finish with todos from todo.md

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel blade coating process resulting in an electrical insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and adapted. 
The recipe was improved by increasing the stability of the solution. 
The process variables were optimized via \gls{emma}. 
%\td{ALSO: How many exp would you over the computer time and effort to find this out?}
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $n_L=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

@@

The concentration can be increased up to 5 times being stable for a minimum of \h{4}. 
The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. 
homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.

>>>>

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel blade coating process resulting in an electrical insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and adapted. 
The recipe was improved by increasing the stability of the solution. 
The process variables were optimized via \gls{emma}. 
%\td{ALSO: How many exp would you over the computer time and effort to find this out?}
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $n_L=10$, $v_{C}=10$, $T_{C}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the number of coating layers has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

@@

The concentration can be increased up to 5 times being stable for a minimum of \h{4}. 
The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. 
Homogeneity can be mainly controlled via blade speed and temperature and layers can be stacked.
